\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.33in, a4paper]{geometry}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}
\thispagestyle{empty}

\noindent
\begin{minipage}[ht]{0.76\linewidth}
{\Huge \textbf{Rodrigo Andrés\\ Maureira Contreras}}\\
{\footnotesize \url{https://linkedin.com/in/ramaureirac} | \url{https://github.com/ramaureirac} | \url{https://t.me/ramaureirac}}

\end{minipage}
\hspace{0.60cm}
\begin{minipage}[ht]{0.29\linewidth}

Valparaíso, Chile.\\
\textbf{56 9 8595 6149\\
ramaureirac@pm.me}

\end{minipage}

\vspace{6mm}

\noindent
Cloud Computing Practitioner with more than one year of experience creating and administrating \textbf{cloud infrastructure}, \textbf{CI/CD} pipelines and \textbf{eliminating toil} on different IT tasks. I also teach computer science students how to pass their university exams.

\vspace{6mm}

\noindent
\begin{minipage}[t]{0.76\linewidth}
\setlist[itemize]{leftmargin=0.425cm}

\subsubsection*{WORKING EXPERIENCE}
\textbf{\href{https://clmdigitalsolutions.com/}{CLM Digital Solutions}:} \textit{Semi Senior Site Reliability Engineer}.\\
{\footnotesize OCTOBER 2021 - NOW.}
\begin{itemize}
    \item[>>] \textbf{Automation} initiative in almost any IT task throught \textbf{Python} or \textbf{Bash}.
    \item[>>] Administration and provisioning of \textbf{AWS} and \textbf{GCP} infrastructure (like GKE, EKS, ECS, VPC, S3, RDS, CloudSQL, etc.) in customers' cloud via \textbf{Terraform}. 
    \item[>>] Experience rising \textbf{technical demos} (PoC) for \textbf{comercial proposals} or \textbf{improvement initiatives} for the current projects.
    \item[>>] \textbf{Infrastructure as code} (IaC) in order to implement a simple \textbf{disaster recovery plan}.
    \item[>>] Deployment of micro-services built with \textbf{NodeJS} (TypeScript) and \textbf{Maven} (Java) for the backend and \textbf{Angular} for the frontend. 
    \item[>>] Design of \textbf{GitLab CI pipelines} for continuous deployment for each environment (GitFlow)
    \item[>>] Responsible for teaching how to use the \textbf{GitLab} in order to deploy new features into different \textbf{Kubernetes} / \textbf{ECS} environments and how to rollback in case something fails.
    \item[>>] Backgrounds working on large IT (\textbf{DevSecOps}) projects for customers like Falabella, WorkMate and Corona. \textbf{Incident resolution} and on-call support
    \item[>>] Very basics of \textbf{ELK} / \textbf{Grafana} for observability and \textbf{SonarQube} for code quality.
\end{itemize}

\vspace{3mm}

\textbf{\href{https://inf.ucv.cl/}{Pontificia Universidad Católica de Valparaíso}:} \textit{Teaching Assistant.}\\
{\footnotesize MARCH 2019 - DECEMBER 2021.}
\begin{itemize}
    \item[>>] Students’ coach and teaching assistant in various computer science courses such as Programming, Computer Networks, Operating Systems and IT Project Administration. 
\end{itemize}

\vspace{3mm}

\textbf{{Freelancer}:} \textit{Site Reliability Engineer, DevOps and Programmer}.\\
{\footnotesize MARCH 2019 - OCTOBER 2021.}
\begin{itemize}
    \item[>>] Freelance at different small business such as PortalEducativo.net, FID Seguros and PrevComp.
    \item[>>] Clean up initiative and \textbf{resources organization} at PortalEducativo.net. Thanks to this our team save up to \$300 per project. Use of \textbf{GCP} and \textbf{GitLab} since day one.
    \item[>>] Leader and main promoter of \textbf{DevOps culture} at FID Seguros Generales. Now the company is able to release features into production in a secure way and as fast as possible.
\end{itemize}

\subsubsection*{PERSONAL PROJECTS}
\vspace{1mm}

\textbf{\href{https://github.com/ramaureirac/godot-tactical-rpg}{Godot Tactical RPG}:} \textit{A 3D tactics game template like FireEmblem, FinalFantasy or XCOM}\\
{\footnotesize JULY 2019 - NOW.}

\subsubsection*{STUDIES, COURSES AND CERTIFICATIONS}
\vspace{1mm}

\textbf{{Pontificia Universidad Católica de Valparaíso}:} \textit{Computer Science \& Engineer Degree.}\\
{\footnotesize MARCH 2016 - DECEMBER 2021.}
\\
\\
\textbf{{Coursera}:} \textit{Preparing for Google Cloud Platform: Cloud DevOps Engineer}\\
{\footnotesize JUNE 2021 - JULY 2021.}
\\
\\
\textbf{{LinkedIn}:} \textit{Prepare for the AWS Certified Cloud Practitioner Exam.}\\
{\footnotesize NOVEMBER 2021 - DECEMBER 2021.}


\end{minipage}
\hspace{0.60cm}
\begin{minipage}[t]{0.29\linewidth}
\setlist[itemize]{leftmargin=0cm}

\subsubsection*{KNOWLEDGE}
\vspace{1mm}

\begin{itemize}
    \item[] CI/CD.
    \item[] Coding (Python, Bash).
    \item[] Cloud Computing.
    \item[] Google Cloud.
    \item[] Amazon Web Services.
    \item[] Canary Deployments.
    \item[] Networking.
    \item[] GNU/Linux.
    \item[] Docker.
    \item[] NGINX
    \item[] Git.
    \item[] GitLab.
    \item[] Jenkins.
    \item[] SonarQube.
    \item[] Kubernetes / ECS.
    \item[] DevOps Culture.
    \item[] SCRUM framework.
    \item[] Incident Resolution.
    \item[] Disaster Recovery Plan.
    \item[] Infrastructure as Code.
    \item[] Monitoring.
\end{itemize}

\subsubsection*{SKILLS}
\vspace{1mm}

\begin{itemize}
    \item[] Teaching.
    \item[] Communication.
    \item[] Self-taught.
    \item[] Teamwork.
    \item[] Critical thinking.
    \item[] Proactive.
    \item[] Improvement initiative.
\end{itemize}


\subsubsection*{LANGUAGES}
\vspace{1mm}

\begin{itemize}
    \item[] Spanish (Native).
    \item[] English (Intermediate).
\end{itemize}

\end{minipage}

\end{document}
